Ch3 process

### 2022-02-17 Ch3_samplesize/Ch3_process.Rmd
Getting ready to run and save this. Monte Carlo sim.

tibble(thresh.vals) %>% 
  mutate(w.cdfs = w.cdfs,
         w.cdfs = round(w.cdfs, 5),
         samp.n = map_dbl(1:length(thresh.vals), function(y) length(which(simplsamps$data >= thresh.vals[y]))),
         samp.p = signif(samp.n/samp.size, 3)) %>% 
  knitr::kable()

@@

for(i in 1:nrow(fevd.mles)){
  ith.n        <- fevd.mles$samp.size[i]
  ith.samples  <- data.frame(x = sample(simplsamps$data, ith.n))
  # Can't use this because by setting those higher thresholds we have one data point and can't fit anything to it. 
  #ith.thresh   <- fevd.mles$threshold[i]

  # So, setting the threshold to 0 so we can compare to Lomax.
  ith.thresh <- 0

  ith.fit      <- fevd(ith.samples$x, threshold = ith.thresh, type = "GP")

@@

@@

```{r}
fevd.mles
```

@@

fevd.mles %>% 
  mutate(ks = 1/shape,
         alphas = scale*ks) %>% 
  dplyr::select(-c(scale, shape)) %>% 
  mutate(est.cdf = lomax.cdf(threshold, alphas, ks),
         tail = 1- est.cdf, 
         mean = lomax.mean(alphas, ks)) -> est.lomax.mles
est.lomax.mles %>% knitr::kable()

@@

And visually, we

>>>>

tibble(thresh.vals) %>% 
  mutate(w.cdfs = w.cdfs,
         w.cdfs = round(w.cdfs, 5),
         samp.n = map_dbl(1:length(thresh.vals), function(y) length(which(simplsamps$data >= thresh.vals[y]))),
         samp.p = signif(samp.n/samp.size, 3)) -> tru.cdfs

tru.cdfs %>% 
  knitr::kable()

@@

for(i in 1:nrow(fevd.mles)){
  ith.n        <- fevd.mles$samp.size[i]
  ith.samples  <- data.frame(x = sample(simplsamps$data, ith.n))

  # So, setting the threshold to 0 so we can compare to Lomax.

  ith.fit      <- fevd(ith.samples$x, threshold = 0, type = "GP")

@@

  ith.thresh   <- fevd.mles$threshold[i]
  fevd.mles$gp.tail[i] <- pextRemes(ith.fit, ith.thresh, lower.tail = FALSE)
}

@@

```{r}
fevd.mles %>% 
  knitr::kable()
```

@@

fevd.mles %>% 
  mutate(ks = 1/shape,
         alphas = scale*ks) %>% 
  #dplyr::select(-c(scale, shape)) %>% 
  mutate(est.cdf = lomax.cdf(threshold, alphas, ks),
         tail = 1- est.cdf, 
         mean = lomax.mean(alphas, ks)) -> est.lomax.mles
est.lomax.mles %>% knitr::kable()

```  
The NaN I get in the previous dataframe are due to 0/0, so, undefined? What should I make of it?

So, now I will estimate the ratio between the estimated cdf and the true cdf.

```{r fig.width=8}

est.lomax.mles %>% 
  mutate(tru.tails = rep(tru.cdfs$w.cdfs, length(samp.sizes)),
         tails.ratio = tail/tru.tails,
         thresh = factor(threshold)) %>%
  drop_na(tails.ratio) %>% 
  mutate(nice.tails = signif(tails.ratio, 3)) %>% 
  ggplot(., aes(x = samp.size, y = tails.ratio, color = thresh)) +
  geom_point() +
  labs(title = "Lomax") +
  theme_minimal() -> lomax.tail

est.lomax.mles %>% 
  mutate(tru.tails = rep(tru.cdfs$w.cdfs, length(samp.sizes)),
         gp.tails.ratio = gp.tail/tru.tails,
         thresh = factor(threshold)) %>%
  mutate(nice.tails = signif(gp.tails.ratio, 3)) %>% 
  ggplot(., aes(x = samp.size, y = gp.tails.ratio, color = thresh)) +
  geom_point() +
  labs(title = "GP")
  theme_minimal() -> gp.tail

plot_grid(lomax.tail, gp.tail)

@@

Now, we repeat the process to see how much this varies...

```{r results='hide'}
nreps <- 100
gp.mles.reps <- data.frame(NULL)

for(j in 1:nreps){

  ith.mle.df <- data.frame(samp.size = rep(samp.sizes, length(thresh.vals)), threshold = thresh.vals,
                           scale = 0, shape = 0, nllh = 0, gp.tail = 0, rep = 0)

  for(i in 1:nrow(ith.mle.df)){
  ith.n        <- ith.mle.df$samp.size[i]
  ith.samples  <- data.frame(x = sample(simplsamps$data, ith.n))

  # So, setting the threshold to 0 so we can compare to Lomax.

  ith.fit      <- fevd(ith.samples$x, threshold = 0, type = "GP")

  ith.mle.df$scale[i] <- mles[1]
  ith.mle.df$shape[i] <- mles[2]
  ith.mle.df$nllh[i]  <- nll.hat
  ith.mle.df$rep[i] <- paste0("rep", j)

  ith.thresh   <- fevd.mles$threshold[i]
  fevd.mles$gp.tail[i] <- pextRemes(ith.fit, ith.thresh, lower.tail = FALSE)

  gp.mles.reps <- rbind.data.frame(gp.mles.reps, ith.mle.df)

}
save.image(gp.mles.reps, "Ch3_samplesize/testdf.RData")
```
